Visual Analytics of Large Bipartite Networks assisted by Multilevel Strategies\thanks{Supported by FAPESP, project 2017/05838-3}

### 2019-05-23 paper.tex
adiantado ate soft implementation

The interactivity is crucial for a number of reasons:
the definition of the uncoarsening phase desired;
for the navigation of the network,
including the access to metadata and changes to the visualization achieved;
for uncoarsening supernodes;
and for tunning the achieved visual mapping status, such as by resizing
and moving nodes.
The overall procedure is delineated in Algorithm~\ref{alg} and further
detailed in Sections~\ref{nav} and~\ref{sof}.

@@

Other operations are convenient to make the visual mapping adequate for the diverse settings possible:
network size, open supervertices, levels exposed, and topological features such as commnity structures.

\noindent 
\section{Software implementation}\label{sof}
%%%
% description of the functionalities/tools implemented,
% of the technologies and libraries used
% optimization of the computational capacity for large networks by
% means of Web GL, triangles for nodes and details on demand

@@

\section{Conclusions and further work}\label{con}
%%%
% extension to multipartite (or heterogeneous) networks.
% use for marking nodes as pivots for coarsening

>>>>

The interactivity is crucial for a number of reasons:
the definition of the uncoarsening phase desired;
for the navigation of the network,
including the access to metadata and changes to the visualization achieved;
for uncoarsening supernodes;
and for tuning the achieved visual mapping status, such as by resizing
and moving nodes.
The overall procedure is delineated in Algorithm~\ref{alg} and further
detailed in Sections~\ref{nav} and~\ref{sof}.

@@

Other operations are convenient to make the visual mapping adequate for the diverse settings possible:
network size, open supervertices, levels exposed, and topological features such as community structures.
The navigations pathway, already as achieved within the software we made available, is illustrated in Figure~\ref{fnav}.

\begin{figure}[!h]\centering
 \includegraphics[width=0.6\textwidth]{fnav}
  \caption{The navigation pathway of the bipartite network obtained through a multilevel strategy
  and auxiliary tools.
  }\label{fnav}
\end{figure}

\noindent 
\section{Software implementation: mlvis}\label{sof}
%%%
% description of the functionalities/tools implemented,
% of the technologies and libraries used
% optimization of the computational capacity for large networks by
% means of Web GL, triangles for nodes and details on demand
We implemented the framework described in Section~\ref{des} using scientific,
database and web resources,
and made the final result available to the user within a web page
for use through simple mouse-driven actions
and requiring the instalation of no software but a web browser such as Firefox or Google Chrome.
The final result is exemplified in Figure~\ref{fpage} and next subsections
describe its functionalities and the technologies used.

\begin{figure}[!h]\centering
 \includegraphics[width=\textwidth]{fpage}
  \caption{The navigation pathway of the bipartite network obtained through a multilevel strategy
  and auxiliary tools.
  }\label{fpage}
\end{figure}

\subsection{The use of mlvis}
% network upload, format.
% layouts available
% algorithms available for coarsening, and their parametrization
% initialization of the visualization: click on render
% tools available and their operation

\subsection{Technologies used within mlvis}
% coarsening algorithms
% flask for server, feather for auxiliary server
% mongodb filesystem for data
% Nuxt/Vue.js for the frontend with heavy use of PIXI.js

@@

% enhancements of the navigation through the use of being-developed coarsening algorithms
% the use of the interface for guiding coarsening (through markers)
% the use of the interface to analyse coarsening results

% technologies used: maybe simpler if using meteor.js
% and simpler to achieve multiuser interactivity

\section{Conclusions and further work}\label{con}
%%%
% extension to multipartite (or heterogeneous) networks.
